A neural coarse graining theory of consciousness

### 2018-06-08 Paper_neural_coarse_graining_of_consciousness.tex
to Martin2

			%% Macroscale Deterministic
			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions \highlightAndComment{at a show time scale}{is this necessary?} are nearly deterministic.\callforhelp{Is there any good ref I can cite?}

@@

			\subsubsection{Hoel's theory\callforhelp{Help from Marting?}}
				\ideaBox{This is very important. Need to be careful here.}

>>>>

			%% Macroscale Deterministic
			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\callforhelp{Is there any good ref I can cite?}

@@

			\subsubsection{Hoel's theory\callforhelp{Help from Martin?}}
				\ideaBox{This is very important. Need to be careful here.}
